Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-08-04 ms.tex
updated software references using the \software command

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$. We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).

@@

>>>>

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree}.
\textbf{We downselected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) \textbf{reference stars} at apparent separations of 5$\arcsec$--30$\arcsec$.
We identified 30 potential targets \textbf{and} prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).

@@

\textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}. SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.}}
